Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
small modifs

\begin{table}[H]
\centering
\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation                & 0.886 & 0.884 & 0.891 & 0.877\\
Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
Our approach               & & & & \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
Our approach + dir         & & & & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\centering
\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
Our approach               & & & & \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
Our approach + dir         & & & & \\
\bottomrule
\end{tabular}
\end{table}
